---
title: "R Notebook"
output: html_notebook
---
Drought was roughly April 2016 - June 2017

Load packages
```{r}
library(ggplot2)
library(tidyverse)
library(lubridate)
library(rnoaa)
library(corrplot)
library(gridExtra)
library(corrr)
```

Load discharge record
```{r}
dat <- read_csv("GribbleGap_Discharge_Record_Full_Clean.csv")
```
Get Precip Data DON'T RUN, HERE TO PRESERVE HOW DATA WAS DOWNLOADED
```{r}
api <- "sCfMUOqzUYDuKbFBzDcXRqpvdDfCmdiw"
loc <- 'GHCND:USC00312200' #cullowhee

ncdc_stations(stationid = loc, token = api)$data$name

years <- c(2014,2015,2016,2017,2018)

for(x in years){

P <- ncdc(datasetid='GHCND', datatypeid = "PRCP", stationid = loc, token = api,
     startdate = paste(x,'-09-30', sep = ''), 
     enddate = paste(x+1,'-09-30', sep = ''), 
     limit = 365)

if(x == 2014) Pall <- P

if(x > 2014) Pall <- bind_rows(Pall, P)
#Pall_BU <- Pall
}

Pall <- select(Pall, date, value)
Pall <- drop_na(Pall)
Pall$Pmm <- Pall$value / 10
write.csv(Pall, "Cullowhee_Precip_Daily.csv")
```

Read in Precip Data
```{r}
P <- read_csv("Cullowhee_Precip_Daily.csv")

ggplot(P, aes(x = date, y = Pmm)) + 
  geom_bar(stat = "identity") +
  scale_y_reverse()
```


Compute daily, weekly, monthly, yearly discharge timeseries
```{r}
#daily
dat %>% group_by(day(time), month(time), year(time)) %>%
    summarize(median(disch)) -> daily

colnames(daily) <- c("day","month","year","medQ")  

daily$date <- dmy(paste(daily$day, daily$month, daily$year))

daily <- ungroup(daily)
daily <- select(daily, date, medQ)

#weekly
dat %>% group_by(week(time), year(time)) %>%
    summarize(median(disch)) -> weekly

colnames(weekly) <- c("week","year","medQ")  

weekly$date <- as.Date(
  paste(weekly$year, weekly$week, 1),
  format = "%Y %U %u"
)

weekly <- ungroup(weekly)
weekly <- select(weekly, date, medQ)

#monthly
dat %>% group_by(month(time), year(time)) %>%
    summarize(median(disch)) -> monthly

colnames(monthly) <- c("month","year","medQ")  

monthly$date <- dmy(paste(1,monthly$month, monthly$year))

monthly <- ungroup(monthly)
monthly <- select(monthly, date, medQ)

#water-yearly

#define water year
#in this script or another, define a water year function
#2016 water year is 10-01-2015 - 9-30-2016
 water_year <- function(date) {
               ifelse(month(date) < 10, year(date), year(date)+1)}
 
 
dat %>% group_by(water_year(time)) %>%
    summarize(median(disch, na.rm = TRUE)) -> yearly

colnames(yearly) <- c("year","medQ")  

yearly$date <- dmy(paste(1,1, yearly$year))

yearly <- ungroup(yearly)
yearly <- select(yearly, date, medQ)
```

Daily, weekly, monthly, yearly precip!
```{r}
#daily
dailyP <- P

#daily
P %>% group_by(day(date), month(date), year(date)) %>%
    summarize(sum(Pmm)) -> dailyP

colnames(dailyP) <- c("day","month","year","Pmm")  

dailyP$date <- dmy(paste(dailyP$day, dailyP$month, dailyP$year))

dailyP <- ungroup(dailyP)
dailyP <- select(dailyP, date, Pmm)

#weekly
P %>% group_by(week(date), year(date)) %>%
    summarize(sum(Pmm)) -> weeklyP

colnames(weeklyP) <- c("week","year","Pmm")  

weeklyP$date <- as.Date(
  paste(weeklyP$year, weeklyP$week, 1),
  format = "%Y %U %u"
)

weeklyP <- ungroup(weeklyP)
weeklyP <- select(weeklyP, date, Pmm)

#monthly
P %>% group_by(month(date), year(date)) %>%
    summarize(sum(Pmm)) -> monthlyP

colnames(monthlyP) <- c("month","year","Pmm")  

monthlyP$date <- dmy(paste(1,monthlyP$month, monthlyP$year))

monthlyP <- ungroup(monthlyP)
monthlyP <- select(monthlyP, date, Pmm)


#yearly -> should probably be water year
water_year <- function(date) {
               ifelse(month(date) < 10, year(date), year(date)+1)}

P %>% group_by(water_year(date)) %>%
    summarize(sum(Pmm)) -> yearlyP

colnames(yearlyP) <- c("year","Pmm")  

yearlyP$date <- dmy(paste(1,1, yearlyP$year))

yearlyP <- ungroup(yearlyP)
yearlyP <- select(yearlyP, date, Pmm)

```



Plot daily, weekly, monthly
```{r}
ggplot(daily, aes(date, medQ))+
  geom_line()

ggplot(weekly, aes(date, medQ))+
  geom_point()

ggplot(monthly, aes(date, medQ))+
  geom_point()

ggplot(yearly, aes(date, medQ))+
  geom_point()

ggplot(yearlyP, aes(x = date, y = Pmm)) + 
  geom_bar(stat = "identity") +
  scale_y_reverse()
```

Plot faceted ggplot with different time periods
```{r, fig.height=8, fig.width = 7}
periods <- bind_rows("daily" = daily,"weekly" = weekly,
                     "monthly" = monthly,"yearly" = yearly,
                     .id = "Period")

periods$Period <- factor(periods$Period, 
                         levels = c("daily", "weekly", "monthly", "yearly"))

ggplot(periods, aes(x = date, y = medQ))+
  geom_line()+
  geom_point()+
  scale_y_log10()+
  facet_grid(rows = vars(periods$Period))
```
Discharge and precip plots
```{r}
#combine P and Q for each time bin THEN bind rows
bdaily <- inner_join(daily, dailyP, by = "date")
bweekly <- inner_join(weekly, weeklyP, by = "date")
bmonthly <- inner_join(monthly, monthlyP, by = "date")
byearly <- inner_join(yearly, yearlyP, by = "date")

periods <- bind_rows("daily" = bdaily,"weekly" = bweekly,
                     "monthly" = bmonthly,"yearly" = byearly,
                     .id = "Period")

periods$Period <- factor(periods$Period, 
                         levels = c("daily", "weekly", "monthly", "yearly"))

#ggplot()+
#  geom_bar(data = periods, aes(date, -Pmm), stat = "identity")+
#  geom_line(data = periods, aes(date, medQ))+
#  facet_grid(Period~., scales = "free_y")
    

```
```{r}
int <- "weekly"

Q <- ggplot(data = subset(periods, Period == int), aes(date, medQ))+
  geom_line()

P <- ggplot(data = subset(periods, Period == int), aes(date, Pmm))+
  geom_bar(stat = "identity")

grid.arrange(Q,P, nrow = 2 )
```
```{r}
int <- "monthly"

Q <- ggplot(data = subset(periods, Period == int), aes(date, medQ))+
  geom_line()

P <- ggplot(data = subset(periods, Period == int), aes(date, Pmm))+
  geom_bar(data = subset(periods, Period == "yearly"), aes(date, Pmm), stat = "identity", alpha = 0.2)+
  geom_bar(stat = "identity")+
  scale_y_reverse()
  

grid.arrange(P,Q, nrow = 2 )
```
Monthly Precip vs Monthly discharge
```{r}
toplot <- periods %>% group_by(Period)

toplot$lag1 <- lag(toplot$Pmm, 1)
toplot$lag2 <- lag(toplot$Pmm, 2)
toplot$lag3 <- lag(toplot$Pmm, 3)
toplot$lag4 <- lag(toplot$Pmm, 4)
toplot$lag5 <- lag(toplot$Pmm, 5)
toplot$lag6 <- lag(toplot$Pmm, 6)

lagswide <- drop_na(toplot)

toplot <- pivot_longer(toplot, c(Pmm, lag1, lag2, lag3, lag4, lag5, lag6), names_to = "Pmm")

toplot <- drop_na(toplot)

toplot <- ungroup(toplot)


ggplot(toplot, aes(value, medQ, color = Pmm))+
  geom_smooth()+
  ylab("Median Q (L/s)")+
  xlab("Precip (mm)")+
  facet_grid(rows = vars(toplot$Period))

#cors <- correlate(lagswide$medQ, lagswide[,3:9])#cor(lagswide$medQ, lagswide[,3:9])
#cors <- data.frame(t(cors))
#colnames(cors) <- "cor"
#cors$lag <- row.names(cors)
#cors$lag <- factor(cors$lag, c("Pmm","lag1","lag2","lag3","lag4","lag5","lag6"))

lagswide <- ungroup(lagswide)

dailycor <- lagswide %>% filter(Period == "daily") 
weeklycor <- lagswide %>% filter(Period == "weekly") 
monthlycor <- lagswide %>% filter(Period == "monthly") 

dcv <- dailycor %>% select(-date, -Period) %>%
     correlate() %>%
     focus(medQ)

wcv <- weeklycor %>% select(-date, -Period) %>%
     correlate() %>%
     focus(medQ)

mcv <- monthlycor %>% select(-date, -Period) %>%
     correlate() %>%
     focus(medQ)

corsall <- bind_rows("days" = dcv, "months" = mcv, "weeks" = wcv, .id = "period")

colnames(corsall) <- c("period","lag","cor")

corsall$lag <- factor(corsall$lag, levels = c("Pmm", "lag1","lag2","lag3","lag4","lag5","lag6"))
corsall$period <- factor(corsall$period, levels = c("days", "weeks","months"))

#ggplot(cors, aes(lag,cor, fill = cor))+
  #geom_bar(stat = "identity")+
  #facet_grid(rows = vars(toplot$Period))
```
```{r, fig.height = 6, fig.width= 4}
ggplot(corsall, aes(lag,cor, fill = cor))+
  geom_bar(stat = "identity")+
  facet_grid(rows = vars(period))+
  theme_classic()
```


